Analyzing Information Transfer from Different Data Sources via Precise Bias-variance Asymptotics

### 2021-07-08 revision_journal/results.tex
finish sec 3.1
sec 4 wip

\section{Main results}

@@

\begin{figure}[!t]
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/verify_covariate_shift.eps}
		\caption{Verify variance asymptotics in finite dimensions}
		\label{fig_sec3_covariate}
	\end{subfigure}
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
		\caption{HPS estimator under covariate shift}
		\label{fig_sec3_covariate}
	\end{subfigure}
	\caption{Figure \ref{fig_sec3_covariate}: we verify that Theorem \ref{thm_main_RMT} provides incredibly accurate estimates of the empirical variance under various finite sample sizes and dimensions.
	Figure \ref{fig_sec3_covariate}: We illustrate an intriguing dichotomy between covariate shift and sample size ratio: The dimension $p = 200$, $n_2 = 800$, and the noise variance $\sigma^2 = 1/4$.}
\end{figure}

@@

    We first describe a setting for modeling covariate shift.
    Let $\cS$ be the set of positive definite matrices $M^{\top} M$ such that for $i = 1,2,\dots,\floor{\frac p 2}$, $\lambda_{p - i}  = \frac 1 {\lambda_i}$, where $\lambda_1 \ge \lambda_2 \ge \cdots \ge \lambda_p$ are the eigenvalues of $M$.
    Under this setting, we ask: suppose that the sample sizes $n_1$ and $n_2$ are both fixed, which $M$ provides the best ``transfer'' in the sense of HPS estimator's excess risk?
    We observe a dichotomy that depends on whether or not $n_1$ is greater than $n_2$.
    \begin{claim}\label{claim_dichotomy}
        Let $g(M) = \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}}$.
        Suppose that $n_1$ and $n_2$ are both fixed.
        Within the set of all possible covariate shift matrix $M$ described above, the following dichotomy holds:
        \begin{enumerate}
	        \item If $n_1 \ge n_2$, then $g(M)$ is minimized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
	        \item If $n_1 < n_2$, then $g(M)$ is maximized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
        \end{enumerate}
    \end{claim}

>>>>

\section{Main results}\label{sec_main}

@@

\begin{figure}[!t]
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/verify_covariate_shift.eps}
		\caption{Verify variance asymptotics in finite dimensions}
		\label{fig_sec3_verify_cov}
	\end{subfigure}
	\begin{subfigure}[b]{0.5\textwidth}
		\centering
		\includegraphics[width=0.9\textwidth]{figures/covariate_shift.eps}
		\caption{Sample size ratios vs. covariate shift}
		\label{fig_sec3_covariate}
	\end{subfigure}
	\caption{Figure \ref{fig_sec3_covariate}: we verify that Theorem \ref{thm_main_RMT} provides incredibly accurate estimates of the empirical variance under various finite sample sizes and dimensions.
	Figure \ref{fig_sec3_covariate}: We illustrate an intriguing dichotomy between covariate shift and sample size ratio: The dimension $p = 200$, $n_2 = 800$, and the noise variance $\sigma^2 = 1/4$.}
	\label{fig_sec31}
\end{figure}

@@

    We first describe a setting for modeling covariate shift.
    Let $\cS$ be the set of positive definite matrices $M^{\top} M$ such that for $i = 1,2,\dots,\floor{\frac p 2}$, $\lambda_{p - i}  = \frac 1 {\lambda_i}$, where $\lambda_1 \ge \lambda_2 \ge \cdots \ge \lambda_p$ are the eigenvalues of $M$.
    Under this setting, we ask: suppose that the sample sizes $n_1$ and $n_2$ are both fixed, which $M$ provides the best ``transfer'' in the sense of HPS estimator's excess risk?
    We observe a dichotomy that depends on whether or not $n_1$ is greater than $n_2$.
    \begin{claim}[Covariate shift vs. sample size ratios]\label{claim_dichotomy}
        Let $g(M) = \frac{\sigma^2}{n_1 + n_2} \bigtr{\frac 1 {\alpha_1 M^{\top} M + \alpha_2}}$.
        Suppose that $n_1$ and $n_2$ are both fixed.
        Within the set of all possible covariate shift matrix $M\in\cS$, the following dichotomy holds:
        \begin{itemize}
	        \item If $n_1 \ge n_2$, then $g(M)$ is minimized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
	        \item If $n_1 < n_2$, then $g(M)$ is maximized in $\cS$ when $\lambda_i = 1$, for any $i = 1,\dots,p$.
        \end{itemize}
    \end{claim}
